---
title: "Text Analyis"
output: github_document
---




# Your mission

Perform text analysis.

## Okay, I need more information

Perform sentiment analysis or topic modeling using text analysis methods as demonstrated in the pre-class work and in the readings.

## Okay, I need even more information.

Do the above. Can't think of a data source?

- `gutenbergr`
- `AssociatedPress` from the `topicmodels` package
- `NYTimes` or `USCongress` from the `RTextTools` package
- Harry Potter Complete 7 Books text
    ```
    if (packageVersion("devtools") < 1.6) {
  install.packages("devtools")
}

devtools::install_github("bradleyboehmke/harrypotter")
    ```
- [State of the Union speeches](https://pradeepadhokshaja.wordpress.com/2017/03/31/scraping-the-web-for-presdential-inaugural-addresses-using-rvest/)
- Scrape tweets using [`twitteR`](https://www.credera.com/blog/business-intelligence/twitter-analytics-using-r-part-1-extract-tweets/)

Analyze the text for sentiment OR topic. **You do not need to do both**. The datacamp courses and [Tidy Text Mining with R](http://tidytextmining.com/) are good starting points for templates to perform this type of analysis, but feel free to *expand beyond these examples*.

# Timelines and Task


We will spend the next 2 weeks working on analyzing textual data in R. You will do the following:

- Start with some text based data.
- Clean data and prepare it for analysis
- Ask questions about the data
- Answer these questions with the data using tables and graphics
- Each group member must have their own unique question that they code the answer for. 

```{r}
  install.packages("devtools")
devtools::install_github("bradleyboehmke/harrypotter")
library("harrypotter")
library("tidyverse")
library("stringr")
library("rebus")
library("tidytext")

# create vector of book names
book_names <- list(philosophers_stone, chamber_of_secrets, prisoner_of_azkaban, goblet_of_fire, order_of_the_phoenix, half_blood_prince, deathly_hallows)
names(book_names) <- c("philosophers_stone", "chamber_of_secrets", "prisoner_of_azkaban", "goblet_of_fire", "order_of_the_phoenix", "half_blood_prince", "deathly_hallows")

# clean data
books = vector(mode = "list", length = 7)
for(i in 1:length(books)){
  # convert text to dataframe
  data <- data_frame(text = book_names[[i]])
  # add column for chapter numbers and title of book
  data <- mutate(data, chapter = c(1:nrow(data)), title = names(book_names)[i])
  # split by word and remove punctuation
  data <- data %>%
    unnest_tokens(word, text, to_lower = TRUE)
  # store clean data to list
  books[[i]] <- data
}

# make one data frame from list of data frames
books <- plyr::ldply(books, data.frame)


```
# Question 1 How the sentiment changes across the entire book
```{r}
POA <- filter(books,title=="prisoner_of_azkaban") %>%
inner_join(get_sentiments("bing")) %>%
group_by(chapter,sentiment) %>%
dplyr::summarize(count=n())

ggplot(POA,aes(x=chapter,y=count,color=sentiment))+
  geom_path() +
  ggtitle("Sentiment Type Per Chapter in Prisoner of Azkaban")+
    scale_color_brewer(palette='Set1')+
  geom_smooth(se=FALSE,linetype = "dashed")
```


# Question 2 What are the most common words by chapter
```{r}
common_words<-books%>%
  filter(title =="prisoner_of_azkaban")%>%
  filter(!(word %in% c("He","I","The"))) %>%
  anti_join(stop_words)%>%
  group_by(chapter)%>%
  dplyr::count(word, sort=TRUE)%>%
  top_n(5)%>%
  arrange(chapter)
common_words
```


#Question 3 Which characters appear the most 
```{r}
# clean data
books = vector(mode = "list", length = 7)
for(i in 1:length(books)){
  # convert text to dataframe
  data <- data_frame(text = book_names[[i]])
  # add column for chapter numbers and title of book
  data <- mutate(data, chapter = c(1:nrow(data)), title = names(book_names)[i])
  # split by word and remove punctuation
  data <- data %>%
  # include upper case words  
    unnest_tokens(word, text, to_lower = FALSE)
  # store clean data to list
  books[[i]] <- data
}

# make one data frame from list of data frames
books <- plyr::ldply(books, data.frame)





POA <- filter(books,title=="prisoner_of_azkaban") %>%
select(word) %>% 
# regular expression for character names
filter(str_detect(word, UPPER %R% ANY_CHAR %R% ANY_CHAR %R% ANY_CHAR)) %>%  
# remove words that aren't character names
filter(!(word %in% c("The","They","What","There","It's","Then"))) %>%
filter(word != "Harry's", word != "Professor", word != "Gryffindor") %>%
# get frequency for most popular character names
group_by(word) %>%
dplyr::summarize(count=n()) %>%
arrange(desc(count))


# Plotting for top 9 names
ggplot(POA[1:9, ],aes(x=reorder(word,count),y=count)) + 
  geom_col(fill="cyan",color="blue") +
  xlab("Characters") +
  ggtitle("Most Popular Characters in Prisoner of Azkaban") +
# Put frequency labels next to bars  
  geom_text(aes(label = paste0(count)), nudge_y = 1) +
  coord_flip()
```

#Question 4 How the emotion anticipation changes throughtout the book
```{r}
total_words =
books %>%
  filter(title=="prisoner_of_azkaban") %>%
  inner_join(get_sentiments("nrc"))%>%
  group_by(chapter,sentiment) %>%
  dplyr::count(word) %>%
  dplyr::summarize(word_occurence=sum(n))%>%
mutate(total_words=sum(word_occurence)) %>%

  filter(sentiment=="anticipation") %>%
  mutate(proportion= word_occurence/total_words) 


ggplot(total_words,aes(x=chapter,y=proportion))+
  ggtitle("Anticipation Throughout Prisoner of Azkaban") +
  geom_line(color="deeppink")
```


#Question 5 Word count for each book
```{r}
filter(books,title=="prisoner_of_azkaban") %>%
select(word) %>% 
dplyr::summarize(total_words=n())
```
















```
