---
title: "Text Analyis"
output: github_document
---




# Your mission

Perform text analysis.

## Okay, I need more information

Perform sentiment analysis or topic modeling using text analysis methods as demonstrated in the pre-class work and in the readings.

## Okay, I need even more information.

Do the above. Can't think of a data source?

- `gutenbergr`
- `AssociatedPress` from the `topicmodels` package
- `NYTimes` or `USCongress` from the `RTextTools` package
- Harry Potter Complete 7 Books text

```{r, message=FALSE, warning=TRUE}

install.packages("devtools")
devtools::install_github("bradleyboehmke/harrypotter")

library(harrypotter)
```
- [State of the Union speeches](https://pradeepadhokshaja.wordpress.com/2017/03/31/scraping-the-web-for-presdential-inaugural-addresses-using-rvest/)
- Scrape tweets using [`twitteR`](https://www.credera.com/blog/business-intelligence/twitter-analytics-using-r-part-1-extract-tweets/)

Analyze the text for sentiment OR topic. **You do not need to do both**. The datacamp courses and [Tidy Text Mining with R](http://tidytextmining.com/) are good starting points for templates to perform this type of analysis, but feel free to *expand beyond these examples*.

# Timelines and Task


We will spend the next 2 weeks working on analyzing textual data in R. You will do the following:

- Start with some text based data.
- Clean data and prepare it for analysis
- Ask questions about the data
- Answer these questions with the data using tables and graphics
- Each group member must have their own unique question that they code the answer for.


```{r}
library(plyr)
library(dplyr)
library(tidytext)
library(stringr)
library(ggplot2)


titles <- c("philosophers_stone", "chamber_of_secrets", "prisoner_of_azkaban", "goblet_of_fire", "order_of_the_phoenix", "half_blood_prince", "deathly_hallows")

books <- list(philosophers_stone, chamber_of_secrets, prisoner_of_azkaban,
           goblet_of_fire, order_of_the_phoenix, half_blood_prince,
           deathly_hallows)
  
series <- tibble()

for(i in seq_along(titles)) {
        
        clean <- tibble(chapter = seq_along(books[[i]]),
                        text = books[[i]]) %>%
             unnest_tokens(word, text) %>%
             mutate(book = titles[i]) %>%
             select(book, everything())

        series <- rbind(series, clean)
}

series
series %>%
  filter (book == "half_blood_prince")
```

(1) How the sentiment changes across the entire book


```{r}
Book6 <- series %>%
  filter (book == "half_blood_prince") %>% 
       inner_join(get_sentiments("afin")) %>%
       group_by(chapter) %>%
       summarise(n= sum(score))
Book6

p1 <- ggplot(Book6, aes(x=chapter, y=n)) +
      geom_line(show.legend = FALSE, size = 0.3, color = "blue") +
      scale_color_brewer(palette = "Set1") +
      geom_smooh(se=FALSE, size = 0.3, linetype = 4, color = "green")

p1+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(),axis.line = element_line(colour = "black") )+
 xlim(1, 30) +
scale_x_continuous(
  breaks = c(1:30)) +
  geom_hline(yintercept = 0, color = "red") +
 ylim(-250, 250) +
  scale_y_continuous(
    breaks = c(seq(-250,250,by=50)) 
  )+ 
  ggtitle("Change in Sentiment in Half-Blood Prince")

```


```{r}
Book6 <- series %>%
  filter (book == "half_blood_prince") %>% 
       inner_join(get_sentiments("afin")) %>%
       group_by(sentiment) %>%
      ungroup() %>%
  group_by(chapter) %>%
  count(sentiment, chapter)
  

p1 <- ggplot(Book6, aes(x=chapter, y=n, color = sentiment)) +
      geom_line(show.legend = FALSE, size = 0.3) +
      scale_color_brewer(palette = "Set1") +
      geom_smooth(se=FALSE, size = 0.2, linetype = 4)

p1 + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(),axis.line = element_line(colour = "black") )+
 xlim(1, 30) +
scale_x_continuous(
  breaks = c(1:30)) +
 ylim(1, 280) +
  breaks = c(seq(1:280, by= ))

```

(2) WHat are the most common words by chapter
```{r}
Book6Word <- series %>%
  filter(book == "half_blood_prince") %>%
  group_by(chapter)  %>%
  anti_join(stop_words) %>%
  count(word, chapter) %>%
  top_n(1)

Book6Word
```

(3) Which characters appear the most 
```{r}
library(dplyr)
Book6Char <- series %>%
         filter(book == "half_blood_prince")  %>%
         group_by(word) %>%
         select(word) %>%
         filter(word == "harry" | 
                word == "ron" | 
                word == "hermione" | 
                word == "dumbledore" |
                word == "voldemort" | 
                word == "dobby") %>%
         count (word, sort = TRUE) %>%
         arrange (desc(n))
           
Book6Char 

ggplot(Book6Char, aes(x=word, y=n)) +
geom_col(show.legend = FALSE, fill = "lightblue", width  = 0.5)
```

(4) How the emotion anticipation changes throughtout the book
```{r}
Book6Anti <- series %>%
  filter (book == "half_blood_prince") %>% 
       inner_join(get_sentiments("nrc"))  %>%
       group_by(chapter) %>%
       count (sentiment) %>%
       filter(sentiment == "anticipation") 
        
Book6Anti

ggplot(Book6Anti, aes(x=chapter, y=n)) +
geom_col(show.legend = FALSE, fill = "blue", width  = 0.5)


```


(5) Word count for each book
```{r}
Book6Count <- series %>%
  filter(book == "order_of_the_phoenix") %>%
  group_by(chapter) 
nrow(book6)
```






