---
title: "Harry Potter Analysis"
output: github_document
---

# Timelines and Task


We will spend the next 2 weeks working on analyzing textual data in R. You will do the following:

- Start with some text based data.
- Clean data and prepare it for analysis
- Ask questions about the data
- Answer these questions with the data using tables and graphics
- Each group member must have their own unique question that they code the answer for. 

# Overview

Harry Potter text analysis to answer the following questions: 

(1) How does the sentiment change across the entire book?
(2) What are the most common words by chapter?
(3) Which characters appear the most?
(4) How does the emotion anticipation change throughout the book?
(5) What is the word count for each book?
(6) Individual Question: How many beasts in the Fantastic Beasts book were mentioned in all the Harry Potter books?


```{r, echo=FALSE, warning=FALSE, message=FALSE}

#Gather libraries
library(plyr)
library(dplyr)
library(tidytext)
library(stringr)
library(stringi)
library(ggplot2)
library(harrypotter)
library(rebus)
library(tokenizers)
library(tm)

#Gather data
book_names <- list(philosophers_stone, chamber_of_secrets, prisoner_of_azkaban, goblet_of_fire, order_of_the_phoenix, half_blood_prince, deathly_hallows)

names(book_names) <- c("philosophers_stone", "chamber_of_secrets", "prisoner_of_azkaban", "goblet_of_fire", "order_of_the_phoenix", "half_blood_prince", "deathly_hallows")

#divide books, put into datasets
books = vector(mode = "list", length = 7)
for(i in 1:length(books)){
  data <- data_frame(text = book_names[[i]])
  data <- mutate(data, chapter = c(1:nrow(data)), title = names(book_names)[i])
  data <- data %>%
    unnest_tokens(word, text, to_lower = TRUE)
  books[[i]] <- data
}


```

## Question 1: How does the sentiment change across the entire book?

In the pre-class assignments, we performed sentiment analysis using text analysis methods. The following sentiment analysis is applied to Goblet Of Fire: 

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#Carol will be working on Goblet of Fire:
#(1) How the sentiment changes across the entire book
bing <- get_sentiments("bing")
cs_book= books[[4]]
sentiment_4=inner_join(cs_book, bing) #merge sentiments
percents <- sentiment_4 %>% dplyr::group_by(chapter) %>% dplyr::count(sentiment) %>% dplyr:: mutate(total_words=sum(n), percent=n/total_words) #get percentage of words 

#plot positives versus negatives
ggplot(percents, aes(x = chapter, y = percent, fill=sentiment)) +geom_bar(stat='identity', color='black')+
  guides(fill=guide_legend(reverse=T)) +
  scale_fill_brewer(palette='Blues')+
  ggtitle("Sentiments Per Chapter")+
  ylab("Percentage") + 
  xlab("Chapter")+
  theme(plot.title = element_text(hjust = 0.5))
```

  
It seems like more the of the chapters seems to be on the "negative" side. 

## Question 2: What are the most common words by chapter?

The most common words in Goblet Of Fire. The graph only contains words that that up 1% or more words per chapter. 

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#(2) What are the most common words by chapter

#create stop words
stop=c(stopwords("en"), 'said', 'mr', 'mrs', 'he', 'she', 'it', 'they', 'i', 'you', 'professor', 'The', 'I', 'He', 'She', 'It', 'will')

#filter out stop words and then get their percentage per chapter, use only words with more than 1% per chapter
comm_words<-cs_book %>% dplyr::filter(!word %in% stop) %>% dplyr::group_by(chapter) %>% dplyr::count(word) %>% dplyr::arrange(desc(n)) %>% dplyr::rename(count=n)%>% dplyr::mutate(total=sum(count), percent=count/total) %>% filter(percent>0.01)

#plot most common words
ggplot(comm_words, aes(x=percent, y=reorder(word, percent)))+
  geom_point(size=1, aes(color=factor(chapter)))+
  theme_classic()+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(), 
        panel.grid.major.y = element_line(color='grey', linetype = "dashed"), 
        plot.title = element_text(hjust = 0.5))+
  ggtitle("Most Common Words In Goblet Of Fire")+
  ylab("Words") + 
  xlab("Mentioned By Percentage of Each Chapter")
```
  
As expected, "harry" is mentioned the most in the book. Surprisingly, though, "Voldemort" is also mentioned quite a few times. Perhaps he isn't the one who shall not be named?

## Question 3: Which characters appear the most?

Similiarly, we can find the most popular characters in the book: 
```{r, echo=FALSE, warning=FALSE, message=FALSE}
#(3) Which characters appear the most 
books = vector(mode = "list", length = 7)
for(i in 1:length(books)){
  data <- data_frame(text = book_names[[i]])
  data <- mutate(data, chapter = c(1:nrow(data)), Title = str_to_title(str_replace_all(names(book_names)[i], "_", " ")))
  data <- data %>%
    unnest_tokens(word, text, to_lower = F)
  books[[i]] <- data
}
#capitalize first letter of each word
cap_stop=stri_trans_totitle(stop)
#create pattern to grab 
pattern1=START %R% UPPER %R% optional(zero_or_more(ANY_CHAR) %R% SPC %R% UPPER)
Char_4<-str_subset(books[[4]]$word, pattern=pattern1)
#create a list of characters and then reduce to unique list
char_list<-data_frame(word=Char_4) %>% filter(!word %in% cap_stop) %>% unique()
#join the characters, calculate percentage per character
char_list_2<-right_join(books[[4]], char_list) %>% dplyr::count(word)  %>% dplyr::arrange(desc(n)) %>% dplyr::filter(n>100)%>% dplyr::mutate(total=sum(n), percent=n/total)

#plot percentages
ggplot(char_list_2, aes(x=percent, y=reorder(word, percent)))+
  geom_point(size=2)+
  theme_classic()+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(), 
        panel.grid.major.y = element_line(color='grey', linetype = "dashed"), 
        plot.title = element_text(hjust = 0.5))+
  ggtitle("Most Appeared Charcters")+
  ylab("Characters Names") + 
  xlab("Mentioned By Percentage of The Book")
```

Of course, Harry, Ron and Hermione are the top three characters in the book. 

## Question 4: How does the emotion anticipation change throughout the book?

Rather than looking at emotional differences in each chapter, we look at the anticipation trend throughout the book.
  
```{r, echo=FALSE, warning=FALSE, message=FALSE}

#(4) How the emotion anticipation changes throughtout the book
#get anticipation
nrc <- get_sentiments("nrc") %>% filter(sentiment=='anticipation')
cs_book= books[[4]]
anti_4=inner_join(cs_book, nrc)#join anticipation
percents_4 <- anti_4 %>% dplyr::group_by(chapter) %>% dplyr::count(sentiment)

#create y-axis marks for labeling
y_label_above=(percents_4$n+10)
y_label_below=(percents_4$n-5)
differences=c(0,diff(percents_4$n))
y_label=rep(0, length(differences))
choose_label=cbind(y_label_below, y_label_above, differences, y_label)
#choose the axis points: if the point is higher than the previous point then place label above the point, if not, then below the point:
y_label=sapply(1:nrow(choose_label), function(x,y) if(y[x,3]>=0){y[x,4]=y[x,2]}else{y[x,4]=y[x,1]}, y=choose_label) 
y_label=data_frame(y_label)
y_label=y_label %>% mutate(chapter=row_number())
percents_4=inner_join(percents_4, y_label) #join the points

#plot points
ggplot(percents_4, aes(x=chapter, y=n, label=n))+
  geom_line(colour="dark blue")+ #add line graph
  geom_point(size=1, shape=21, fill='white')+ #make points white
  stat_smooth(method=loess, se=F, colour="grey")+
  geom_text(aes(y=y_label, label=n), vjust=1.5, color='black')+   ggtitle("Changes in Anticipation")+
  ylab("Anticipation") + 
  xlab("Chapter")+
  theme(plot.title = element_text(hjust = 0.5))
```

Anticipation peaked at around Chapter 24.   

## Question 5: What is the word count for each book?

```{r, echo=FALSE, warning=FALSE, message=FALSE}

#(5) Word count for each book
word_count=c(rep(0,7))
for(i in 1:7){
  word_count[i]<-books[[i]] %>% dplyr::summarise(total_words=n())
}
word_count=data_frame(word_count=unlist(word_count))
word_count=bind_cols(data_frame(Title=str_to_title(str_replace_all(names(book_names), "_", " "))), word_count)
q5<-word_count

#plot points
ggplot(q5, aes(x=Title, y=word_count))+
  geom_bar(stat='identity', aes(fill=Title))+ 
  ggtitle("Number Of Words Per Book")+
  ylab("Number of Words") + 
  xlab("Book")+
  theme(plot.title = element_text(hjust = 0.5))+ 
  coord_flip()
```


Order Of The Pheonix, Deathly Hallows and Half Blood Prince are the wordiest books in the Harry Potter series.

## Question 6: Individual Question: How many beasts in the Fantastic Beasts book were mentioned in all the Harry Potter books?
```{r, echo=FALSE, warning=FALSE, message=FALSE}

#(6) Individual Question: How many beasts in the Fantastic Beasts book were mentioned in all the Harry Potter books?

#list the beasts
beasts<-c('Acromantula'
,'Ashwinder' 
,'Augurey' 
,'Basilisk' 
,'Billywig'
,'Bowtruckle'
,'Bundimun'
,'Centaur'
,'Chimaera'
,'Chizpurfle'
,'Clabbert'
,'Crup'
,'Demiguise'
,'Diricawl'
,'Doxy'
,'Dragon'
,'Opaleye'
,'Fireball'
,'Hebridean'
,'Horntail'
,'Ridgeback'
,'Vipertooth'
,'Longhorn'
,'Short-Snout'
,'Ironbelly'
,'Dugbog'
,'Erkling'
,'Erumpent'
,'Fairy'
,'Crab'
,'Flobberworm'
,'Fwooper'
,'Ghoul'
,'Glumbumble'
,'Gnome'
,'Graphorn'
,'Griffin'
,'Grindylow'
,'Hidebehind'
,'Hippocampus'
,'Hippogriff'
,'Hodag'
,'Horklump'
,'Imp'
,'Jarvey'
,'Jobberknoll'
,'Kappa'
,'Kelpie'
,'Knarl'
,'Kneazle'
,'Leprechaun'
,'Lethifold'
,'Lobalug'
,'Malaclaw'
,'Manticore'
,'Merpeople'
,'Moke'
,'Mooncalf'
,'Murtlap'
,'Niffler'
,'Nogtail'
,'Nundu'
,'Occamy'
,'Phoenix'
,'Pixie'
,'Plimpy'
,'Pogrebin'
,'Porlock'
,'Puffskein'
,'Quintaped'
,'Ramora'
,'Red Cap'
,'Reem'
,'Runespoor'
,'Salamander'
,'Serpent'
,'Shrake'
,'Snallygaster'
,'Snidget'
,'Sphinx'
,'Streeler'
,'Tebo'
,'Thunderbird'
,'Troll'
,'Unicorn'
,'Wampus'
,'Werewolf'
,'Winged horse'
,'Yeti')
beasts=data_frame(word=beasts, beasts=beasts)

#join the beasts in each book
#join the beasts in each book
hpbeasts<-lapply(1:7, function(x) inner_join(books[[x]], beasts))
hpbeasts<-bind_rows(hpbeasts) #put the lists into one dataset
hpbeasts <- hpbeasts %>% dplyr::group_by(Title) %>% dplyr::count(beasts) %>% dplyr:: mutate(total_words=sum(n), percent=n/total_words, y_label=cumsum(percent))

#plot beasts mentioned, stacked by title
ggplot(hpbeasts, aes(x = beasts, y = n)) +
  geom_bar(stat='identity', aes(fill=Title))+
  theme(axis.text.x = element_text(size=.05)) +
  ggtitle("Fantastic Beasts in Harry Potter Series")+
  ylab("Number of Times Mentioned") + 
  xlab("Beasts")+
  theme(plot.title = element_text(hjust = 0.5))+
  coord_flip()

 
```
  
Fantastic Beasts and Where To Find Them is a guide of beasts in the Harry Potter world. As expected, some of the beasts in the guide would be mentioned in the Harry Potter book series. But how many of them are mentioned and how many of them are mentioned in each book? The above graph shows a list of beasts mentioned in the books, indexed by book. For example, "Phoenix" is mentioned the most in The Order Of The Phoenix; "Horntail" is mentioned the most in Goblet Of Fire. 
