---
title: "Text Analyis"
output: github_document
---

# Your mission

Perform text analysis.

## Okay, I need more information

Perform sentiment analysis or topic modeling using text analysis methods as demonstrated in the pre-class work and in the readings.

## Okay, I need even more information.

Do the above. Can't think of a data source?

- `gutenbergr`
- `AssociatedPress` from the `topicmodels` package
- `NYTimes` or `USCongress` from the `RTextTools` package
- Harry Potter Complete 7 Books text

- [State of the Union speeches](https://pradeepadhokshaja.wordpress.com/2017/03/31/scraping-the-web-for-presdential-inaugural-addresses-using-rvest/)
- Scrape tweets using [`twitteR`](https://www.credera.com/blog/business-intelligence/twitter-analytics-using-r-part-1-extract-tweets/)

Analyze the text for sentiment OR topic. **You do not need to do both**. The datacamp courses and [Tidy Text Mining with R](http://tidytextmining.com/) are good starting points for templates to perform this type of analysis, but feel free to *expand beyond these examples*.

# Timelines and Task


We will spend the next 2 weeks working on analyzing textual data in R. You will do the following:

- Start with some text based data.
- Clean data and prepare it for analysis
- Ask questions about the data
- Answer these questions with the data using tables and graphics
- Each group member must have their own unique question that they code the answer for. 

# Cleaning the data 
```{r}
book
```
# Questions for analysis: 

1. By ordering the frequency of the word that appears(remove stop words), could you find the word that appears most frequently?
```{r}
tidy_freq
```
2. By doing sentiment analysis, which sentiment word is most likely to be used by author?
```{r}
sentiment_likely
```
3. By dividing into two groups, which word is used most frequently in each group?
```{r}
bing_freq
```
4. Can you draw wordcloud picture of the stone book?
```{r}
tidy_stone2
```
5. Can you draw a picture of the percentage of the word?
```{r}
stone_word
```
6. What is the relationship between the rank and frequency?
```{r}
freq_by_rank
```
7. Could you divide the text by bigrams rather than words?
```{r}
bigram_counts
bigram_united
```
8. What is the tf_idf of the bigram_united we create in last question?
```{r}
bigram_tf_idf
```
9. Can you show the word after the negative word?
```{r}
not_words
negated_words
```
10. Draw the picture of the relationship between different words, using arrows to show the relation.
```{r}
bigram_graph
bigram_ggraph
```
11. What is the correlation between each word?
```{r}
word_cor
```
12. What are the top words appear in each of the book?
```{r}
top_book
```
13. Dividing by books, what is the top joy words in each of them?
```{r}
top_joy_book
```
14. Dividing by books, what is the top "sadness" words in each of them?
```{r}
top_sad_book
```
15. What is the ratio of the positive word and negative word in each book according to the chapter?
```{r}
ratio
```
16. What is the difference of negative words and positive words in each book according to the chapter?
```{r}
diff
```
