---
title: "Intitial Work"
output: html_document
---



## Setting up for grabbing this Data

## Setup

```{r, eval=FALSE}

## This function checks the installed packages on local computer and installs if already not installed and loads them  
source("sadia/check_packages_SS.R")
package_check(c("dplyr","ggplot2","gutenbergr","stringr", "stringi", "tidytext", "tidyr", "gridExtra", "SnowballC", "wordcloud", "RColorBrewer"))

# dplyr # for data manipulation
# ggplot2 # for graphs
# gutenbergr # to download gutenberg books
# stringr, stringi # for text analysis
# tidytext, tidyr #for tidying the data
# gridExtra # to arrange multiple plots in one page
# SnowballC # for text stemming
# wordcloud # word-cloud generator 
# RColorBrewer # color palettes
```


## Initial Scraping

We downloaded the books with the "gutenberg_download" function of gutenbergr package. "gutenbergr" package has other functions like:

- "gutenberg_metadata" that shows information about each work, pairing Gutenberg ID with title, author, language, etc and 
- "gutenberg_authors" that shows information about each author, such as aliases and birth/death year.

#My textual data: 
-Alice's adventure in wonderland is a fantasy novel written by Lewis Carroll, narrating the story of little "Alice" who fells through the rabbit hole into a fantasy world. The book has total 13 chapters and I am trying to analyze the change of emotions throughout the book as alice expererienced different adventures in her wonderland! 

-Finally, I will compare this book with the books of my other team members (Picture of Dorian Gray choosen by Catrina; and Quran, Bible and The Essence of Buddhism choosen by Ze) to see the variation of sentiments in different genre books



The following function will download the books and save in a list `booklist.rda` in the `data_SS` folder
```{r, eval=FALSE}
get_book <- function(bookID){
  #Create directory, if it already exists then dont show warnings.
  # This eliminates the need for setwd
  # running my code will create these files whereever you store this data in
  dir.create("sadia/data_SS/", showWarnings = FALSE)
  
  booklist <- list() #list of dataframes that will contain all the 5 books
  for (i in 1:length(bookID)){
    booklist[[i]] <- gutenberg_download(bookID[i]) #download one by one and save in the list
    save(booklist, file="sadia/data_SS/booklist.rda")
  }
  # print(booklist) debug print
}
get_book(bookID)
```


Here are the book ids to download 5 books that will be analyzed by our team:
```{r, eval=FALSE}
bookID <-c(751, 174, 2800, 10, 18223)
# 751: Alice's Adventure in Wonderland (I will analyze this book)
# 174: Picture of Dorian Gray (Cat will analyze this book)
# 2800: Quran (Ze will analyze this books)
# 10: Bible (Ze will analyze this books)
# 18223: The Essence of Buddhism (Ze will analyze this books)
get_book(bookID)
```

We can see the structure of the booklist by taking the `.rda` file:
```{r, eval=TRUE}
load("data_SS/booklist.rda")
str(booklist) #We can then see that what we have a list of 5 books with the texts of each book in a dataframe
```

As the next step, we have cleaned the books (removing spaces, punctuations, arranging by chapter) and created a data frame of all books `tidy_books.rda`:

```{r, eval=FALSE}
clean_book <- function(bookID){
  load("sadia/data_SS/booklist.rda")
  tidy_books <- list()
  for (i in 1:length(bookID)){
    tidy_books[[i]] <- booklist[[i]] %>%mutate(linenumber = row_number(), chapter = cumsum(str_detect(text,regex("chapter|CHAPTER[\\divxlc]", 
                    ignore_case = TRUE)))) %>% unnest_tokens(word, text)
     }
  save(tidy_books, file = "sadia/data_SS/tidy_books.Rda")
  #print( str(tidy_books)) #debug print
}

clean_book(bookID)
```


We now have a data frame output from this. We then create the following files containing functions and analysis from this data:

```
01_get_packages_SS.R   # install the required packages
02_get_books_SS.R    # download the books
03_clean_books_SS   # clean the books
04_join_sentiment_SS   # join with the lexicon for sentiment analysis
05_graphs_SS     # create the graphs
06_paper_SS     # create the final paper containg the results of analysis
```
 



